Computing Entropies with Nested Sampling

### 2017-10-17 talk/ms.tex
Minor fixes

\begin{enumerate}
\item<2-> Entropy of the prior for the parameters $H(\theta)$
\item<3-> Entropy of the conditional prior for the data $H(\theta | d)$
\item<4-> Entropy of the posterior $H(\theta | d)$
\item<5-> Entropy of the prior for the data $H(d)$
\end{enumerate}

@@

\begin{block}{Remark}
{\em Conditional entropies} such as (2) and (3)
are defined using an expectation over the quantity conditioned upon.
\end{block}

>>>>

\begin{enumerate}
\item<2-> Entropy of the prior for the parameters $H(\theta)$
\item<3-> Entropy of the conditional prior for the data $H(d | \theta)$
\item<4-> Entropy of the posterior $H(\theta | d)$
\item<5-> Entropy of the prior for the data $H(d)$
\end{enumerate}

@@

\begin{block}{Remark}
{\em Conditional entropies} such as (2) and (3)
are defined using an expectation over the second argument
(the thing conditioned on).
\end{block}
